---
title: "Alcohol vs Seat choice"
author: "Michelle Benavides"
date: "July 7, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

According to the Fancy Notch Boxplot, the mean, first quartile, and third quartile for the "Back" seat boxplot are significantly higher as  compared to the "front" and "Middle" seats. The "Front" seat data seems to have the lowest median and maximum, while the "Middle" data has the most outliers. The people in the "Back" seats seemed to have consumed more alcohol than the people in the "Front" and "Middle" seats. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

According to the numerical summary, there seems to be almost three times as many people in the "Middle" seats compared to the people in the "Back" and "Front" seats. However, the "Back" row has consumed about four times as much units of alcohol compared to all other people. 

## Inferential Tests

## Conclusions


