---
title: "Alcohol vs Seat choice"
author: "Michelle Benavides"
date: "July 7, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

According to the Fancy Notch Boxplot, the mean, first quartile, and third quartile for the "Back" seat boxplot are significantly higher as  compared to the "front" and "Middle" seats. The "Front" seat data seems to have the lowest median and maximum, while the "Middle" data has the most outliers. The people in the "Back" seats seemed to have consumed more alcohol than the people in the "Front" and "Middle" seats. 

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

According to the numerical summary, there seems to be almost three times as many people in the "Middle" seats compared to the people in the "Back" and "Front" seats. However, the "Back" row has consumed about four times as much units of alcohol compared to all other people. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The inferential results show a low p-value, indicated that there is an issue in the data, which warrants further statistical testing through a TurkeyHSD test. 

```{r}
plot(TukeyHSD(model1))
```

According to the TurkeyHSD model, the Front-Back difference consistently yields and negative number, indicating that there is an actual difference between the alcohol consumption  of the Front rows and that of the Middle rows; this observation also persists for the Middle-Back data. The differences between  the Middle and the Front rows aren't as large compared to the other two categories, even passing zero at an instance, showing that the Middle and the Front rows are not very different from one another. 

## Conclusions


